### 2017-11-06 Cars/paper.tex
ID tags

\begin{itemize}
\item Modern cars are able to track lane marking and can calculate distance to other cars in relative co-ordinates (Thuy and Leon 2010)
\item Data from NGSIM is in coordinates relative to start of road - no impact of the curvature of the lane
\item Fit curve to car data to estimate lane midpoints (Woo et. al. 2016) 
\begin{enumerate}
\item At each point in time $t$ calculate the total distance each car has travelled along the road using $d_{i, t} = \sum_{s=1}^t v_{i, s}$, where $v_{i, s}$ is the velocity of car $i$ at time $s$. 
\item Estimate polynomial functions of the form $x_{i, t} = f(d_{i, t})$ and $y_{i, t} = g(d_{i, t})$, where $x_{i, t}$ and $y_{i, t}$ are the car coordinates relative to the start of the road.
\item Use polynomials to get $\hat{x}_{i, t}$ and $\hat{y}_{i, t}$ as estimates of the midpoint of the lane after travelling a distance $d_{i, t}$.
\item Define new coordinates 
\begin{align}
x^*_{i, t} &= \sqrt{(x_{i, t}-\hat{x}_{i, t})^2 + (y_{i, t} - \hat{y}_{i, t})^2)} \label{xRel} \\
y^*_{i, t} &= d_{i, t} \label{yRel}
\end{align}
\end{enumerate}
\item Note: This should be calculated separately for each lane.
\end{itemize}

>>>>

\begin{itemize}
\item Modern cars are able to track lane marking and can calculate distance to other cars in relative co-ordinates (Thuy and Leon 2010)
\item Data from NGSIM is in coordinates relative to start of road - no impact of the curvature of the lane
\item Fit curve to car data to estimate lane midpoints (Woo et. al. 2016) 
\begin{enumerate}
\item At each point in time $t$ calculate the total distance each car has travelled along the road using $d_{i, t} = \sum_{s=1}^t v_{i, s}$, where $v_{i, s}$ is the velocity of car $i$ at time $s$. 
\item Estimate smoothing splines of the form $x_{i, t} = f(d_{i, t})$ and $y_{i, t} = g(d_{i, t})$, where $x_{i, t}$ and $y_{i, t}$ are the car coordinates relative to the start of the road.
\item Use polynomials to get $\hat{x}_{i, t}$ and $\hat{y}_{i, t}$ as estimates of the midpoint of the lane after travelling a distance $d_{i, t}$.
\item Define new coordinates 
\begin{align}
x^*_{i, t} &= \sqrt{(x_{i, t}-\hat{x}_{i, t})^2 + (y_{i, t} - \hat{y}_{i, t})^2)} \label{xRel} \\
y^*_{i, t} &= d_{i, t} \label{yRel}
\end{align}
\end{enumerate}
\item Note: This should be calculated separately for each lane, cars used to estimate splines are excluded from further modelling
\end{itemize}
